Supporting Information for "Imperfect slope measurements drive overestimation in geometric models of lake depth"

### 2021-02-15 manuscript/si_template_2019.tex
scrub wrr material from supplement, closes #25
more detail to table s1 caption

\title{Supporting Information for "Geometric models overestimate lake depth due to imperfect slope
measurement"}
%
% e.g., \title{Supporting Information for "Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$"}
%
%DOI: 10.1002/%insert paper number here%

@@

% source at tables/01_predictors.Rmd
\begin{table}
\caption{Summary of lake characteristics for the present study (and for lakes in the contiguous United States). Predictor variables for computing random forest offsets (Equation 2) are printed in bold face. Dashes (-) indicate an identical sample size among this study and that of the contiguous United States.} \label{tableS1}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt
\begin{tabular}{lllll}
\hline
Variable & Median & Q25 & Q75 & n\\
\hline
Max depth (m) & 8.2 (7) & 4.6 (3.7) & 14 (12) & 4820 (17700)\\
\textbf{Area (ha)} & 55 (33) & 21 (11) & 140 (100) & 4820 (17700)\\
\textbf{Island area (ha)} & 0 (0) & 0 (0) & 0.18 (0.076) & 4820 (17700)\\
\textbf{Perimeter (m)} & 4400 (3500) & 2500 (1800) & 8100 (7300) & 4820 (17700)\\
\textbf{Shoreline development} & 1.7 (1.7) & 1.4 (1.4) & 2.1 (2.2) & 4820 (17700)\\
\textbf{Elevation (m)} & 300 (340) & 180 (210) & 400 (460) & 4820 (17700)\\
\textbf{Watershed-lake ratio} & 7.8 (10) & 3.8 (4.4) & 17 (29) & 4820 (17700)\\
\textbf{Deepest point distance (m)} & 180 (-) & 110 (-) & 290 (-) & 4820 (-)\\
Mean deepest point distance (m) & 140 (-) & 87 (-) & 230 (-) & 4820 (-)\\
\textbf{Visual center distance (m)} & 240 (-) & 160 (-) & 390 (-) & 4820 (-)\\
Inlake slope (m/m) & 0.05 (-) & 0.02 (-) & 0.08 (-) & 4820 (-)\\
Inlake slope online (m/m) & 0.06 (-) & 0.03 (-) & 0.14 (-) & 4800 (-)\\
Inlake slopes (m/m) & 0.06 (-) & 0.03 (-) & 0.1 (-) & 4820 (-)\\
Inlake slopes online (m/m) & 0.07 (-) & 0.03 (-) & 0.15 (-) & 4800 (-)\\
Mean inlake slope (m/m) & 0.04 (-) & 0.02 (-) & 0.09 (-) & 4820 (-)\\
Nearshore mean slope (m/m) & 0.08 (-) & 0.05 (-) & 0.11 (-) & 4820 (-)\\
Nearshore slope online (m/m) & 0.08 (-) & 0.04 (-) & 0.13 (-) & 4590 (-)\\
Nearshore slopes online (m/m) & 0.08 (-) & 0.04 (-) & 0.13 (-) & 4540 (-)\\
\hline
\end{tabular}
\end{table}

>>>>

\title{Supporting Information for "Imperfect slope measurements drive overestimation in geometric models of lake depth"}
%
% e.g., \title{Supporting Information for "Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$"}
%
%DOI: 10.1002/%insert paper number here%

@@

% source at tables/01_predictors.Rmd
\begin{table}
\caption{Summary of lake characteristics for the present study (and for lakes in the contiguous United States). Predictor variables for computing random forest offsets (Equation 2) are printed in bold face. Dashes (-) indicate an identical sample size among this study and that of the contiguous United States from the National Hydrography Dataset. The total number lakes is reported as n.} \label{tableS1}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt
\begin{tabular}{lllll}
\hline
Variable & Median & Q25 & Q75 & n\\
\hline
Max depth (m) & 8.2 (7) & 4.6 (3.7) & 14 (12) & 4820 (17700)\\
\textbf{Area (ha)} & 55 (33) & 21 (11) & 140 (100) & 4820 (17700)\\
\textbf{Island area (ha)} & 0 (0) & 0 (0) & 0.18 (0.076) & 4820 (17700)\\
\textbf{Perimeter (m)} & 4400 (3500) & 2500 (1800) & 8100 (7300) & 4820 (17700)\\
\textbf{Shoreline development} & 1.7 (1.7) & 1.4 (1.4) & 2.1 (2.2) & 4820 (17700)\\
\textbf{Elevation (m)} & 300 (340) & 180 (210) & 400 (460) & 4820 (17700)\\
\textbf{Watershed-lake ratio} & 7.8 (10) & 3.8 (4.4) & 17 (29) & 4820 (17700)\\
\textbf{Deepest point distance (m)} & 180 (-) & 110 (-) & 290 (-) & 4820 (-)\\
Mean deepest point distance (m) & 140 (-) & 87 (-) & 230 (-) & 4820 (-)\\
\textbf{Visual center distance (m)} & 240 (-) & 160 (-) & 390 (-) & 4820 (-)\\
Inlake slope (m/m) & 0.05 (-) & 0.02 (-) & 0.08 (-) & 4820 (-)\\
Inlake slope online (m/m) & 0.06 (-) & 0.03 (-) & 0.14 (-) & 4800 (-)\\
Inlake slopes (m/m) & 0.06 (-) & 0.03 (-) & 0.1 (-) & 4820 (-)\\
Inlake slopes online (m/m) & 0.07 (-) & 0.03 (-) & 0.15 (-) & 4800 (-)\\
Mean inlake slope (m/m) & 0.04 (-) & 0.02 (-) & 0.09 (-) & 4820 (-)\\
Nearshore mean slope (m/m) & 0.08 (-) & 0.05 (-) & 0.11 (-) & 4820 (-)\\
Nearshore slope online (m/m) & 0.08 (-) & 0.04 (-) & 0.13 (-) & 4590 (-)\\
Nearshore slopes online (m/m) & 0.08 (-) & 0.04 (-) & 0.13 (-) & 4540 (-)\\
\hline
\end{tabular}
\end{table}
